\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-08-29 coqimpl.tex
Reorganizing Coqimpl.tex

\textbf{Overridable Field and Closing Fact}
It is natural to consider the ``automatic overridden'' resulting inheritance, as we are using the same tactic (or the same untyped Gallina term to provide the proof). But for type theorists, these are definitely overriding because these are definitely different typed Gallina term!

Instead of making a decision here, we introduce "Closing Fact":  "Closing Fact" will make a field tied with the untyped proof script and only allows inheritance. Of course, during inheritance, the untyped proof script will always be re-run and introduce (potentially) \textbf{different} typed terms\footnote{Thus called "Closing Fact" as its semantic depends on the closed  surrounding family in a global sense}. Thus, we encourage the user to use it in a proof-irrelevant way, where the difference between typed terms can be ignored. Then, the ``automatic overridden'' will always lead to overriding.

This is similar to "FRecursor"---we only allow inheritance for "FRecursor" as its semantic can be considered as a tie between a handler family and an extensible inductive type, where during each inheritance, the tie will be rechecked.

Just like "Overridable .. pins {..}", "Closing Fact" provides the ability to stab through all the abstraction of the former fields, and thus has the similar functionality  as "Overridable .. pins {..}".

@@

\textbf{Hack: ``Meta-data''.} Due to our implementation of the family,
the family data is invisible to Coq internal and thus causes some
inconvenience. For example, in
\cref{fig:plugin-example-global-reasoning-meta-data} the first attempt
of defining tactic "inv" fails. Because the earlier defining "tm",
"value", and "value_not_app" are currently just data structure in the
plugin and not visible for Coq internal (only visible after the family
is compiled into module).

>>>>

\textbf{Escape Hatches: "Meta-data" and "Closing Fact".} There are cases the developers want to refer to global reasoning or just escape from the programming paradigm of family polymorphism. Thus we provide the following mechanism.

\textit{"MetaData".} Due to our implementation of the family,
the family data is invisible to Coq internal and thus causes some
inconvenience. For example, in
\cref{fig:plugin-example-global-reasoning-meta-data} the first attempt
of defining tactic "inv" fails. Because the earlier defining "tm",
"value", and "value_not_app" are currently just data structure in the
plugin and not visible for Coq internal (only visible after the family
is compiled into module).

\textit{"Closing Fact".} We have described how to use partial recursor to "discriminate" different constructors of an extensible inductive type. Practically, "discriminate" is used when proving inversion lemma, like forementioned "var_not_value".

% \textbf{Overridable Field and Closing Fact}
% It is natural to consider the ``automatic overridden'' resulting inheritance, as we are using the same tactic (or the same untyped Gallina term to provide the proof). But for type theorists, these are definitely overriding because these are definitely different typed Gallina term!

% Instead of making a decision here, we introduce "Closing Fact":  "Closing Fact" will make a field tied with the untyped proof script and only allows inheritance. Of course, during inheritance, the untyped proof script will always be re-run and introduce (potentially) \textbf{different} typed terms\footnote{Thus called "Closing Fact" as its semantic depends on the closed  surrounding family in a global sense}. Thus, we encourage the user to use it in a proof-irrelevant way, where the difference between typed terms can be ignored. Then, the ``automatic overridden'' will always lead to overriding.

% This is similar to "FRecursor"---we only allow inheritance for "FRecursor" as its semantic can be considered as a tie between a handler family and an extensible inductive type, where during each inheritance, the tie will be rechecked.

% Just like "Overridable .. pins {..}", "Closing Fact" provides the ability to stab through all the abstraction of the former fields, and thus has the similar functionality  as "Overridable .. pins {..}".

@@
